---
title: "TREC: tree reduced ensemble clustering"
author: "Wenqing Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette we go through how to use this package. Nowadays clustering becomes more and more important in data science area. Lots of applications such as finding patterns, exploratory data analysis and grouping data together make use of clustering algorithms. People have developed a variety of clustering techniques such as k-means, hierarchical clustering, dbscan, etc to cluster the data. However, different algorithms produce different clustering results, and it's very hard to distinguish which it's better. Also, when you produce clustering results from different algorithms, there is also a problem to combine all these clustering results together. TREC stands for tree reduced ensemble clustering, which is an effective algorithm to combine your clustering results together and produce one final clustering.

## How to use TREC


## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
